Storm surges in the Strait of Georgia simulated with a regional model

### 2015-05-11 AO_guides/manuscriptAO.tex
Added Porlire pass

The modelled domain extends from the Strait of Juan de Fuca to Puget Sound to Johnstone Strait (Figure \ref{fig:domain}). Bathymetry from the Cascadia physiography data set \citep{haugerud1999digital} was smoothed to limit large changes in depth across grid cells, so that $\Delta h/\bar{h} \leq 0.8$, where $\Delta h$ is the difference in depth between two adjacent grid cells and $\bar{h}$ is their average depth. For model stability, additional smoothing at the Strait of Juan de Fuca western boundary was imposed to achieve constant depth across the first ten grid cells. As depicted in Figure \ref{fig:domain}, the numerical grid is rotated $29^{\circ}$ counter-clockwise of North in order to maintain computational efficiency since currents within the Strait of Georgia are mainly aligned with this rotated axis. {\color{red} A magnified image of the complex passages through the San Jaun and Gulf Islands is provided in Figure \ref{fig:zoom}.}

The curvilinear orthogonal numerical grid has been divided into 398 by 898 by 40 grid cells, which results in an almost uniform horizontal resolution with grid spacing approximately 440 m by 500 m. The 40 vertical $z$-levels were stretched gradually in order to achieve higher resolution in the surface layer, with 1 m vertical grid spacing down to about 10 m in depth. Below 10 m the grid was stretched to a maximum grid spacing of 27 m in the lowest layer. At the bottom boundary, partial $z$-levels were used in order to limit large changes in bathymetry across grid cells \citep{madec2012nemo}.

>>>>

The modelled domain extends from the Strait of Juan de Fuca to Puget Sound to Johnstone Strait (Figure \ref{fig:domain}). Bathymetry from the Cascadia physiography data set \citep{haugerud1999digital} was smoothed to limit large changes in depth across grid cells, so that $\Delta h/\bar{h} \leq 0.8$, where $\Delta h$ is the difference in depth between two adjacent grid cells and $\bar{h}$ is their average depth. For model stability, additional smoothing at the Strait of Juan de Fuca western boundary was imposed to achieve constant depth across the first ten grid cells {\color{red} inward from the open boundary}. As depicted in Figure \ref{fig:domain}, the numerical grid is rotated $29^{\circ}$ counter-clockwise of North in order to maintain computational efficiency since currents within the Strait of Georgia are mainly aligned with this rotated axis. {\color{red} A magnified image of the complex passages through the San Jaun and Gulf Islands is provided in Figure \ref{fig:zoom}.}

The curvilinear orthogonal numerical grid has been divided into 398 by 898 by 40 grid cells, which results in an almost uniform horizontal resolution with grid spacing approximately 440 m by 500 m. The 40 vertical $z$-levels were stretched gradually in order to achieve higher resolution in the surface layer, with 1 m vertical grid spacing down to about 10 m in depth. Below 10 m the grid was stretched to a maximum grid spacing of 27 m in the lowest layer. At the bottom boundary, partial $z$-levels were used in order to limit large changes in bathymetry across grid cells \citep{madec2012nemo}. {\color{red} Model constraints require that all passages be at least two grid points wide.  This restriction required choices in either widening or closing narrow straits.  In particular, Active Pass was closed and Porlier Pass was widened.  Shallow regions were represented by constant depth of 4 m.  All of these compromises are expected to have significant effects locally but minimal effects on the large scale.}
